
% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage[skip=0pt]{parskip}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, parsep=0pt, partopsep=0pt}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}


% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Aakash Choudhary} \\[7.5pt]
\small
\href{https://in.linkedin.com/in/aakash-choudhary-a8b999192}{\raisebox{-0.05\height}\faLinkedin\ Aakash} \ $|$ \
\href{mailto:aakashc.work@gmail.com}{\raisebox{-0.05\height}\faEnvelope\ aakashc.work@gmail.com} \ $|$ \
\href{tel:+91-9027219749}{\raisebox{-0.05\height}\faMobile\ +91-9027219749} \ $|$ \
\href{https://medium.com/@aakashc.dev}{\raisebox{-0.05\height}\faMedium\ @aakashc.dev} \ $|$ \
\href{https://github.com/ifaakash}{\raisebox{-0.05\height}\faGithub\ ifaakash} \\
\end{tabularx}
%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
\section{Summary}
Results-driven SRE/DevOps Engineer with 4+ years of experience in cloud infrastructure automation, CI/CD, and container orchestration across AWS and Azure. Proficient in Terraform, Docker, Kubernetes, and ECS for scalable, highly available deployments. Experienced in FinOps practices, AWS MAP program management, and data engineering with Azure Data Factory. Exploring GenAI/LLM-powered automation to enhance monitoring, debugging, and operational workflows.
\section{Work Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{DevOps Engineer, Particle41} & \hfill \text{Feb 2025 - Present} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*]
\item Managed cloud infrastructure using Terraform and GitHub Actions, leading to a 30\% improvement in deployment efficiency and infrastructure consistency across environments.
\item Deployed and maintained Azure Data Factory and Databricks components, improving data processing reliability by 50\% and reducing ETL failure rates.
\item Enabled migration of large-scale databases (~1 TB) with minimal downtime, handling both homogeneous and heterogeneous migrations.
\item Migrated applications from .NET Core to .NET Framework, containerized them, and deployed using AWS CodePipeline and CodeBuild.
\item Built Docker images in CodeBuild and managed complex networking setups where all traffic was routed via AWS Transit Gateway, ensuring secure and efficient data flow.
\item Designed and implemented cost-saving strategies for low-traffic or idle virtual machines, achieving up to 40\% monthly cost reduction in non-critical workloads.
\item Created robust CI/CD pipelines with automated triggers and branching strategies, decreasing deployment time by 50\% and enhancing release reliability.
\item Integrated SonarCloud and CodeRabbit into the CI pipeline, enabling automated and secure code quality analysis on pull requests, reducing code review effort by almost 80\%.
\item Architected and deployed AWS ECS-based services for highly available infrastructure, ensuring seamless scaling and fault tolerance for production workloads.
\item Led AWS MAP (Migration Acceleration Program) funding initiatives, collaborating with the AWS Cost team to align business requirements with cost optimization strategies and secure project funding.
\item Managed database migrations using AWS DMS and Amazon MSK, enabling reliable streaming and replication of large-scale data across heterogeneous environments with minimal downtime.
\item Integrated GenAI/LLM tools into batch scripts to enhance monitoring alerting, automate log analysis, and accelerate debugging workflows across environments.
\item Delivered DevOps and cloud infrastructure solutions for clients including Outcomes (healthcare/pharmacy technology platform serving 48,000+ pharmacies) and Optic Systems (property inspection technology company leveraging GPS and 360-degree video systems).
\end{itemize}
} \\
\textbf{SRE/DevOps Engineer, Sopra Steria India} & \hfill \text{July 2022 - Feb 2025} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*]
\item Led and implemented enterprise-wide DevOps initiatives, including migration of on-premises infrastructure to AWS and Azure cloud platforms, resulting in improved scalability and 25\% cost reduction through automated resource management.
\item Built and optimized CI/CD pipelines with GitLab CI/CD, reducing deployment time by 35\%.
\item Designed microservices architecture with Docker and EKS/AKS, improving availability by 50\%.
\item Established comprehensive monitoring and observability framework using Prometheus, Grafana, and Datadog, implementing custom dashboards and alerting policies that improved incident response time by 25\% and enabled proactive system health management.
\item Implemented Infrastructure as Code using Terraform for multi-cloud environments, creating reusable modules and automating configuration management, reducing manual intervention by 50\% and achieving consistent infrastructure deployment.
\item Developed and maintained automation scripts using Python, Bash, and PowerShell for routine operational tasks, including log analysis and security compliance checks, improving team efficiency by 30\%.
\end{itemize}
} \\
\end{tabularx}
\vspace{-\baselineskip} % Reduce space after the section
%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\href{https://github.com/ifaakash/QuickSpin}{Quick Spin}} & \hfill \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*]
\item Built an EC2 launch pad that combines Terraform and Ansible, allowing users to define instance count, type (public/private), and software dependencies (Java, NGINX, Apache, OpenSSH) in a single YAML file — deploying fully configured instances with one click.
\end{itemize}
} \\
\textbf{\href{https://github.com/ifaakash/ai_commit}{AI Committer}} & \hfill \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*]
\item CLI tool that suggests Git commit messages using a locally-run LLM or API key, streamlining version control workflows for the DevOps team.
\end{itemize}
} \\
\textbf{\href{https://github.com/ifaakash/gh-prune}{GitHub Pruner}} & \hfill \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*]
\item CLI tool that cleans up GitHub Actions cache, workflow lists, and stale runs to keep repository history tidy and reduce storage overhead.
\end{itemize}
} \\
\textbf{Raspberry Pi Homelab} & \hfill \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*]
\item Set up a self-hosted infrastructure on Raspberry Pi running Forgejo (Git forge) and k3s (lightweight Kubernetes), managing networking and port configurations for hands-on DevOps experimentation.
\end{itemize}
}
\end{tabularx}
%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}>{\bfseries}l X@{}}
Cloud Platforms: & AWS (EC2, S3, VPC, IAM, RDS, ECS, Glue, Lambda, EKS, DMS, MSK, CloudWatch), Azure (VMs, AKS, Blob Storage, VNets, Azure AD) \\
Data Engineering: & Azure Data Factory, Azure Data Lake Storage, AWS DMS, Amazon MSK \\
Infrastructure as Code (IaC): & Terraform (Cloud resource configurations) \\
Containerization \& Orchestration: & Docker, Kubernetes (EKS/ECS), k3s \\
CI/CD: & GitHub Actions, GitLab CI/CD, AWS CodePipeline \\
Configuration Management: & Ansible (Playbook automation, role management) \\
Monitoring \& Observability: & Prometheus, Grafana, Datadog, Coralogix, Sentry \\
Linux \& Networking: & Linux administration, networking fundamentals, port management, firewall configuration \\
Scripting/Programming: & Bash (Automation scripting), Python, Java \\
GenAI/LLM: & LLM-powered automation in shell scripts, AI-assisted debugging and monitoring \\
Version Control: & Git, Forgejo (self-hosted) \\
Database Technologies: & SQL (Database management, querying) \\
\end{tabularx}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
\textbf{Bachelor’s Degree in Computer Science and Engineering (CSE)}, ABESIT & \hfill \normalsize (2018 - 2022) \\
\end{tabularx}
%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}X@{}}
\begin{itemize}[leftmargin=*]\setlength{\itemsep}{0pt}
\item HashiCorp Certified: Terraform Associate (003) \href{https://www.credly.com/badges/f1d5c44f-f2c8-4e31-93eb-f94f44282e97/linked_in_profile?trk=public_profile_certification-title}{click here}
\item Microsoft Certified: Azure Fundamentals AZ-900 \href{https://www.credly.com/badges/18cfe8ff-55b4-45cf-8ba6-9b3c17c51133/linked_in_profile?trk=public_profile_see-credential}{click here}
\item AWS Certified Solutions Architect – Associate
\end{itemize}
\end{tabularx}
\section{Additional Roles \& Contributions}
\begin{tabularx}{\linewidth}{@{}l X@{}} 
\textbf{Technical Writer, Plain English} & \hfill \text{June 2025 – Present} \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*]
\item Writing and publishing technical articles for a Medium publication with over 3.5M+ readers, focusing on DevOps, cloud infrastructure, and automation.
\end{itemize}
}
\end{tabularx}
\section{Professional Interests}
\begin{tabularx}{\linewidth}{@{}X@{}}
\begin{itemize}[leftmargin=*]
\item Technical writing on platforms like Medium and dev.to, covering DevOps, cloud, and automation topics.
\item FinOps practices and cloud cost optimization for production environments.
\item Exploring GenAI/LLM integration to elevate DevOps automation and observability workflows.
\item Self-hosting and homelab experimentation with Raspberry Pi, Forgejo, and k3s.
\item Building open-source tools that improve DevOps workflows and infrastructure efficiency.
\end{itemize}
\end{tabularx}
\end{document}